{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-29 paper.tex
WIP update related work

\uwds is specifically inspired by the geometric and temporal reasoner
{\sc Spark} (\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.
{\sc Spark} acts as a situation assessment reasoner that generates symbolic
knowledge from the geometry of the environment with respect to relations between
objects, robots and humans. It also takes into account the different perspective
that each agent has on the environment. {\sc Spark} embeds a
modality-independent geometric model of the environment that serves both as
basis for the fusion of the perception modalities and as bridge with the
symbolic layer~\cite{lemaignan2016artificial}. This geometric model is built
from 3D CAD models of the objects, furniture and robots, and full body, rigged
models of humans.  It is updated at run-time by the robot's sensors.
Likewise, \uwds embeds a grounded amodal model of the environment, updated
online from the robot's sensors (sensor fusion).

However, {\sc Spark} is a monolithic module that does not support sharing its
internal 3D model with other external components. In contrast, \uwds focuses on
offering a shared and distributed representation of the environment within the
robot's software architecture.

@@

\subsection{Representing Alternative States of the Environment}

>>>>

\uwds is specifically inspired geometric and temporal reasoner like {\sc Spark}
(\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.  {\sc Spark}
acts as a situation assessment reasoner that generates symbolic knowledge from
the geometry of the environment with respect to relations between objects,
robots and humans. It also takes into account the different perspective that
each agent has on the environment. {\sc Spark} embeds a modality-independent
geometric model of the environment that serves both as basis for the fusion of
the perception modalities and as bridge with the symbolic
layer~\cite{lemaignan2016artificial}. This geometric model is built from 3D CAD
models of the objects, furniture and robots, and full body, rigged models of
humans. It is updated at run-time by the robot's sensors.  Likewise, \uwds
embeds a grounded amodal model of the environment, updated online from the
robot's sensors (sensor fusion).

However, {\sc Spark} is a monolithic module that does not support sharing its
internal 3D model with other external components. In contrast, \uwds focuses on
offering a shared and distributed representation of the environment within the
robot's software architecture. This also distinguishes \uwds from complex
cognitive toolkits like KnowRob (as found in OpenEASE~\ref{beetz2015open}).
While these tools maintain a spatio-temporal model of the world, this model is
internal and not meant to be made widely accessible to other external processes.
\uwds focuses instead on reusability and sharing of distributed spatio-temporal
models.  As such, \uwds can be seen as a middleware for spatio-temporal world
models and, contrary to KnowRob, it does \emph{not} provide any high-level
processing or reasoning capability (this is left to the users).

@@

\subsection{Representing Alternative States of the World}
